The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-24 paper.tex
update

 Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
 demonstrates that there is a sharp pressure jump at $z=3.62$ kpc,\
 indicating that the pressure jump is an expanding reverse shock.\
 The high density upstream of the reverse shock requires\
 an even higher density downstream, i.e. a dense shell formation.\
 Continuing outward, the higher density must match with low density further downstream;\
 thus there exists a contact discontinuity ($z=3.75$ kpc).

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump and dense shell at $z=3.61$ kpc\
             indicate that the innermost bubbles\
             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
             are an expanding reverse shock.\
     }
    \label{fig__profile}
  \end{figure}

>>>>

 Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
 demonstrates that there is a sharp pressure jump at $z=3.62$ kpc,\
 indicating that the pressure jump is an expanding reverse shock.\
 The high density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, the higher density must match with low density further downstream;\
 thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump at $z=3.62$ kpc\
             indicate that the innermost bubbles\
             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
             are an expanding reverse shock.\
             The high density upstream of the reverse shock requires\
             an even higher density downstream.\
             Continuing outward, the higher density must match with low density further downstream;\
             thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).
     }
    \label{fig__profile}
  \end{figure}
